---
  title: "Reproducible Research: Peer Assessment 1"
  output: 
  html_document:
  self_contained: true
  keep_md: true
---
  
  
## Loading and preprocessing the data
  
### set working directery and read in data
```{r}
library(ggplot2)
setwd("C:/Users/leip/Desktop/Reproducible Research/RepData_PeerAssessment1")
unzip(zipfile = "activity.zip")
activity<-read.csv("activity.csv", header=T, na.strings = "NA")
```

## What is mean total number of steps taken per day?
### 1. Calculate the total number of steps taken per day
```{r}
Dsum <-aggregate(activity[,'steps'], by=list(activity$date), FUN=sum, na.rm=TRUE)
names(Dsum) <- c("Date","Sum.step")
```

### 2. Make a histogram of the total number of steps taken each day
```{r TotalStepDay}
qplot(Sum.step, data=Dsum, geom="histogram", binwidth = 1000,
      xlab="Total number of steps taken each day")
```

### 3. Calculate and report the mean and median of the total number of steps taken per day
```{r}
Dmean <- aggregate(activity[,'steps'], by=list(activity$date), FUN=mean, na.rm=TRUE)
names(Dmean) <- c("Date","Mean.step")
Dmedian <- aggregate(activity[,'steps'], by=list(activity$date), FUN=median, na.rm=TRUE)
names(Dmedian) <- c("Date","Median.step")
merge(Dmean, Dmedian, "Date")
```
  
## What is the average daily activity pattern?
### 1. Time series plot of the 5-minute interval (x-axis) and the average number of steps taken, 
###    averaged across all days (y-axis)
```{r AvgStepInterval}
Iavg <- aggregate(activity[,'steps'], by=list(activity$interval), FUN=mean, na.rm=TRUE)
names(Iavg) <- c("Interval","Mean.step")


plot2 <- ggplot(Iavg, aes(Interval, Mean.step)) + geom_line() +
          xlab("5-minute Interval") + ylab("Average Steps Across All Days")
plot2
```

### 2. Which 5-minute interval, on average contains the maximum number of steps?
```{r}
Iavg[which(Iavg$Mean.step==max(Iavg$Mean.step)),  ]
```

## Imputing missing values
### 1. Calculate and report the total number of missing values in the dataset 
###    (total number of row of NAs)
```{r}
missing <- activity[activity$steps == 'NA', ]
### Number of obs is num of missing values
str(missing)
```

### 2. Imputing missing values (impute with mean).
### 3. Create a new dataset with the missing data imputed.
```{r}
library(Hmisc)
activity.imputed <- activity
activity.imputed$steps <- with(activity.imputed, impute(steps, mean))
```

### 4. Make a histogram of the total number of steps taken each day and 

```{r imputed_SumStep}
Dsum.imp <-aggregate(activity.imputed[,'steps'], by=list(activity.imputed$date), FUN=sum, na.rm=TRUE)
names(Dsum.imp) <- c("Date","Sum.step")

qplot(Sum.step, data=Dsum.imp, geom="histogram", binwidth = 1000,
      xlab="Total number of steps taken each day (after imputing)")
```

###    Calculate and report the mean and median total number of steps taken per day
```{r}
Dmean.imp <- aggregate(activity.imputed[,'steps'], by=list(activity.imputed$date), 
                       FUN=mean, na.rm=TRUE)
names(Dmean.imp) <- c("Date","Mean.step")

Dmedian.imp <- aggregate(activity.imputed[,'steps'], by=list(activity.imputed$date), 
                        FUN=median, na.rm=TRUE)
names(Dmedian.imp) <- c("Date","Median.step")

merge(Dmean.imp, Dmedian.imp, "Date")
```

## Are there differences in activity patterns between weekdays and weekends?
### 1. Create a factor variable in the dataset with two levels- "weekday" and "weekend"
```{r}
weekday.yn <- function(date) {
  day <- weekdays(date)
  if (day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))
    return("weekday")
  else if (day %in% c("Saturday", "Sunday"))
    return("weekend")
  else
    stop("invalid date")
}

activity.imputed$date.fmt <- as.Date(activity.imputed$date)
activity.imputed$day.type <- as.factor(sapply(activity.imputed$date.fmt, FUN=weekday.yn))
```

### 2. Make a panel plot of time series plot of the 5-min interval(x) and the avg steps,
###    across weekdays or weekend days (y).
```{r Panel_Wkday_steps}
meansteps <- aggregate(activity.imputed$steps, 
                       by = list(activity.imputed$interval, activity.imputed$day.type), 
                       FUN=mean)
names(meansteps) <- c("interval", "day.type", "steps")
xyplot(steps ~ interval | day.type, meansteps, type = "l", layout = c(1, 2), 
       xlab = "Interval", ylab = "Number of steps")
```